Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-30 Geometric types.tex
Clean up statement of Theorem 5.2

\begin{theorem}\label{thm:geotypes}
Let $\oK^i$, $\orho^0$ and $\varphi^i$, be a Yu type datum, with $i=0,\ldots, d$, satisfying Hypotheses~\ref{H0} and \ref{H1}.
There is an element $\cs{F}_i$ in the Grothendieck group of conjugation equivariant Weil sheaf complexes on $G^i$, tensored with ${\bar\QQ}$, such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, where $\orho_i$ is the representation of $\oK^i$ constructed from the Yu type datum in Section~\ref{ssec:review}, for $i=0,\ldots, d$.
\end{theorem}

>>>>

\begin{theorem}\label{thm:geotypes}
Let $(\oK^i, \orho^0, \varphi^i)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.  Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathcal{K}_{\bar\QQ} D_{G^i}(X)$ such that
\[
\trFrob{\cs{F}_i} = \trace(\orho_i).
\]
\end{theorem}
